A new machine-learning-based prediction of survival in patients with end-stage liver disease

### 2022-11-27 analysis/article.Rmd
docs: typo

We compared `r n_lrns` different statistical and machine-learning
algorithms using the *mlr3* framework
[@mlr3; @R-mlr3; @mlr3proba2021; @R-mlr3proba].
The algorithms used were designed for analysis of survival data:
Cox proportional hazards regression model
[@cox1972; @survival-book; @R-survival];
penalized regressions,
namely, two different implementations of the
lasso (least absolute shrinkage and selection operator) regression
[@tibshirani1997; @glmnet2011; @R-glmnet; @penalized2010; @R-penalized],
two different implementations of the
ridge regression [@glmnet2011; @R-glmnet; @penalized2010; @R-penalized], and
the elastic net regression [@glmnet2011; @R-glmnet];
two different random forest implementations
[@ranger2017; @R-ranger; @randomForestSRC2008; @R-randomForestSRC];
extreme gradient boosting [@chen2016; @R-xgboost];
two different support vector machines [@vanbelle2011; @R-survivalsvm];
;nd two neural networks [@katzman2018; @kvamme2019; @R-survivalmodels].

>>>>

We compared `r n_lrns` different statistical and machine-learning
algorithms using the *mlr3* framework
[@mlr3; @R-mlr3; @mlr3proba2021; @R-mlr3proba].
The algorithms used were designed for analysis of survival data:
Cox proportional hazards regression model
[@cox1972; @survival-book; @R-survival];
penalized regressions,
namely, two different implementations of the
lasso (least absolute shrinkage and selection operator) regression
[@tibshirani1997; @glmnet2011; @R-glmnet; @penalized2010; @R-penalized],
two different implementations of the
ridge regression [@glmnet2011; @R-glmnet; @penalized2010; @R-penalized], and
the elastic net regression [@glmnet2011; @R-glmnet];
two different random forest implementations
[@ranger2017; @R-ranger; @randomForestSRC2008; @R-randomForestSRC];
extreme gradient boosting [@chen2016; @R-xgboost];
two different support vector machines [@vanbelle2011; @R-survivalsvm];
and two neural networks [@katzman2018; @kvamme2019; @R-survivalmodels].
